% Template for ICIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}


\usepackage{spconf,amsmath,graphicx}
\usepackage{epstopdf}


\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\makeatletter
    \newcommand\fcaption{\def\@captype{figure}\caption}
\makeatother
% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{SKETCHPOINTNET: A FASTER MICRO NEURAL NETWORK FOR SKETCH RECOGNITION}
%
% Single address.
% ---------------
\name{Author(s) Name(s)}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Sketch recognition has been studied for years. In previous works, sketches are only treated as images, which ignores the sparse nature of sketches. In this paper, we treat each sketch as a series of track points and propose a neural network to recognize it. Our network, termed as SketchPointNet, achieve highest recognition accuracy among point-based sketch recognition approaches. It uses a hierarchically architecture to summarize the pattern of sketches gradually. And this captures the features of different level. Evaluation are performed on TU-Berlin benchmark. SketchPointNet has less trainable parameters because of shared architectures. 
\end{abstract}

\begin{keywords}
Sketch recognition, recognition speed, model size, SketchPointNet
\end{keywords}

\input{introduction}
\input{approach}
\input{experiments}
\input{conclusion}
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

\end{document}
