%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{clrscode}
\usepackage{url}
\usepackage{color}


 
 
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}
\makeatletter
    \newcommand\fcaption{\def\@captype{figure}\caption}
\makeatother


\newcommand{\cxj}[1]{\textcolor[rgb]{1.00,0.00,0.00}{(cxj: #1)}}
\newcommand{\mdf}[1]{\textcolor[rgb]{0.00,0.00,1.00}{#1}}
\newcommand{\comments}[1]{}
\newcommand{\vb}[1]{\mathbf{#1}}
\begin{document}

\mainmatter
\title{Fusing Human Faces}
\author{Xianxiang Wang and Xuejin Chen}
\institute{University of Science and Technology of China, 230031 Hefei, China\\
\url{kowo@mail.ustc.edu.cn, xjchen99@ustc.edu.cn}}
%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\maketitle


\begin{abstract}

\mdf{Face editing technology has drawn extensive attention for decades and now is widely used in many applications.} 
%
In this paper, we propose an algorithm to fuse features of a source face into another target face. 
There are two main challenges in this task. 
The first challenge is how to rearrange facial features of the target face properly according to the source face. 
The second challenge is to keep hues and illumination information of the target face as much as possible so that the output face looks more natural. 
%
\cxj{One sentence about the main idea, and explain our algorithm pipeline.}
%
Our algorithm contains two steps: \mdf{face alignment and appearance fusion}. 
First, we align two faces according to their facial landmarks, which provide the size, location and distribution of facial features of the two faces.
The two faces are aligned by two meshes generated by Delaunay triangulation according to their facial landmarks.
% and warp the corresponding triangles of two faces into the same shape. 
Second, we fuse the appearance of the source face with the target face in gradient domain. 
%With one face image as target image and reconstructed gradients, we generate fused face by seamless clone. 
We propose an algorithm to reconstruct the new face gradients by preserving the weaker gradients of the target face. 
\cxj{What is the novelty of the proposed method??}
%
Our experiments show that proposed method generates natural-looking faces while preserves lots of illumination information and facial hues of target faces.
%

\keywords{Face fusion, Facial landmarks, Delaunay triangulation, Gradient-based editing}
\end{abstract}


\input{Introduction}
\input{RelatedWork}
\input{Algorithm}
\input{Experiments}
\input{Conclusions}
\input{Refs}





\end{document}
