% Template for ICIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}


\usepackage{spconf,amsmath,graphicx}
\usepackage{epstopdf}


\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\makeatletter
    \newcommand\fcaption{\def\@captype{figure}\caption}
\makeatother
% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{SKETCHPOINTNET: A FASTER MICRO NEURAL NETWORK FOR SKETCH RECOGNITION}
%
% Single address.
% ---------------
\name{Author(s) Name(s)}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Speeding up sketch recognition becomes more important nowadays. Accompanied by the rapid development of mobile and portable devices, more sketch recognition tasks are performed on these platforms. Mobile devices have limited computing resources. So it is vital to reduce the recognition model size and accelerate recognition speed. In previous works, sketches are only treated as images, which ignores the sparse nature of sketches. In this paper, we treat each sketch as a series of track points and propose a neural network to recognize it. Our network, termed as SketchPointNet, uses a hierarchically architecture to summarize the pattern of sketches gradually. And this captures the features of different level. Evaluation are performed on TU-Berlin benchmark. SketchPointNet has a higher recognition speed and a smaller model size than the stat-of-the-art approach. Besides, accuracy of SketchPointNet is x\% which is close the the stat-of-the-art method.
\end{abstract}

\begin{keywords}
Sketch recognition, recognition speed, model size, SketchPointNet
\end{keywords}

\input{introduction}
\input{relatedwork}
\input{approach}
\input{experiments}
\input{conclusion}
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

\end{document}
